An Improved ANS Transaction Template

### 2018-01-26 paper.tex

\subsubsection{Case 2}
The case 2 is design is also limited to 30 cascades in the scenario (limit of
the JCPOA agreement), all design the same way. In thsi case the explored design
aims to reproduce the different stage of the reference case over the different
level of cascade enrichment: the goal is to have the tails assay of a stage to
match the feed assay of the previous stage. To do so instead of aiming for a
S/E stages of 4/10, a S/E stages repartition of 6/7 was targeted.:w

The design properties are:\\
- less than 169 centrifuges per cascade,\\
- F/P/T assays: 0.0071/0.0296/0.002.\\% to be correct with the correct value --
                                      % this corresponds to a S/E of 5/6
The corresponding design is:\\
- 167 centrifuges,\\
- F/P/T assays: 0.0071/0.0260104/0.0019111.\\

Both case 1 and 2 will be simulation without and with tail recycling. In the
tail recycling cases, the tails of the cascade level $N$ are blended in the feed
of cascade level $N-1$.

>>>>

\subsubsection{Case 2}
The case 2 is design is also limited to 30 cascades in the scenario (limit of
the JCPOA agreement), but this time each level of cascade are designed to get
feed with the previous level product and to have 4 stripping stages and 10
enriching stages. The configuration of the different level of cascade can be
found in table \ref{tab:cascadelvl}. The different cascades don't have the same
geometry: the number of centrifuges per stage depends on their own design and
varies slightly from a level to another.

\begin{table}[htb]
\centering
\begin{tabular}{lllll}
\toprule

Level   &           & Assay     &       & Machines  \\ 
        & Feed      & Product   & Feed  &           \\
\midrule
1       & 0.0071    & 0.0413    & 0.0029 & 167       \\
2       & 0.0413    & 0.2043    & 0.0173 & 169       \\
3       & 0.2043    & 0.5941    & 0.0971 & 168       \\
4       & 0.5941    & 0.8834    & 0.3915 & 168       \\
5       & 0.8834    & 0.9735    & 0.7746 & 169       \\

\bottomrule
\end{tabular}
  \caption{Summary of the different properties of the different level of cascade.}
  \label{tab:cascadelvl}
\end{table}
